The reference model approach in feature selection problems \vspace{.1in}

### 2019-05-31 paper/ref_approach.tex
SESE/SSE independent of n

\text{SSE}&=\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
\text{SESE}&=\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j}=\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}] \label{eq:SESE}

@@

where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expactations. Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates. \cite{paper:EBmed} use a mixture of a delta distribution in zero and a heavy-tailed distribution, when this is a Laplace distribution they show an interesting thresholding property of the median estimator and thus present a complete selection procedure using their prior. We include in our comparison such method using the R-package \textit{EbayesThresh} together with the control of the local false discovery rate \citep{book:efron, paper:efron}, using the R-package \textit{locfdr}, and a simple selection procedure using inclusion probability at 0.9 for the HDP posterior credible intervals using the regularised horseshoe prior. All these methods provide a complete selection procedures, we compare the result using or not a reference model on top of the procedure evaluating the average false discovery rate (i.e. ratio of the number of non-relevant selected features over the number of selected features) and the average sensitivity (i.e. ratio of the number of relevant selected features over the total number of relevant features). We also provide a comparison of the stability of the selection using the measure proposed by \cite{paper:stability}.

@@

\hypertarget{shrinkage-signal}{%
\subsubsection{Shrinkage and signal analysis}\label{shrinkage-signal}}
In the framework of full-Bayes methods we analyse the effect of the reference model using two continuous hierarchical shrinkage priors: the Dirichlet-Laplace \citep{paper:dirichlet_laplace} and the regularised horseshoe prior \citep{paper:rhs}. Although the horseshoe+ prior by \cite{paper:horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection. We used an uniform prior on $(1/p,1/2)$ for the Dirichlet hyperparameter of the Dirichlet-Laplace prior, whereas regarding the reguelarised horseshoe prior we followed the indication provided in \cite{paper:rhs} setting the prior guess of the effective number of parameters equal to 1 to achieve the highest shrinkage.

@@

Figure \ref{fig:posterior_intervals} shows an example of posterior distributions for the model \eqref{eq:normal_means_problem2} using the regularised horseshoe prior. Respectively on the right and on the left the results using or not the reference model approach. It is evident how the reference model helps in tearing apart the signals from the noise, resulting in less biased estimates. This is quantified in Figure \ref{fig:SESE_SSE} where average SESE and SSE are depicted after 100 simulations. We observe that the reference approach (in orange) has a clear lower error estimate for both the SESE and the SSE. As $n$ and $\rho$ grow, the amount of error diminish, as expected, when using the reference model, whereas it unexpectedly increases when it is not used \hl{(WHY??)}. We also note that the two priors seem to achieve very similar results, regardless of the approach used.

>>>>

\text{SSE}&=\frac{1}{\sqrt{n-3}}\sum_{j=1}^{p}(\hat{\theta}_{j} - \theta^{0}_{j})^{2} \label{eq:SSE} \\
\text{SESE}&=\frac{1}{\sqrt{n-3}}\sum_{j=1}^{p}\int_{\mathbb{R}}(\theta_{j}-\theta^{0}_{j})^{2}p(\theta_{j}|z_{1},..,z_{p})d\theta_{j} \\
&=\frac{1}{\sqrt{n-3}}\sum_{j=1}^{p}\mathbb{E}_{\theta_{j}}[(\theta_{j}-\theta^{0}_{j})^{2}|z_{1},..,z_{p}] \label{eq:SESE}

@@

where $\theta_{j}^{0}=\sqrt{n-3}\,T_{F}(\rho_{j})$ is the true value, $\hat{\theta}_{j}$ is the posterior median of each parameter $\theta_{j}$ and \eqref{eq:SESE} is a sum of posterior expactations. We divide the errors by $\sqrt{n-3}$ to have quantities independent of the number of statistical units. Note that the quantity SESE takes in account also the uncertainty, thus the shrinkage, of the posterior distributions, whereas the SSE measures only the bias in the point estimates. \cite{paper:EBmed} use a mixture of a delta distribution in zero and a heavy-tailed distribution, when this is a Laplace distribution they show an interesting thresholding property of the median estimator and thus present a complete selection procedure using their prior. We include in our comparison such method using the R-package \textit{EbayesThresh} together with the control of the local false discovery rate \citep{book:efron, paper:efron}, using the R-package \textit{locfdr}, and a simple selection procedure using inclusion probability at 0.9 for the HDP posterior credible intervals using the regularised horseshoe prior. All these methods provide a complete selection procedures, we compare the result using or not a reference model on top of the procedure evaluating the average false discovery rate (i.e. ratio of the number of non-relevant selected features over the number of selected features) and the average sensitivity (i.e. ratio of the number of relevant selected features over the total number of relevant features). We also provide a comparison of the stability of the selection using the measure proposed by \cite{paper:stability}.

@@

\hypertarget{shrinkage-signal}{%
\subsubsection{Shrinkage and signal analysis}\label{shrinkage-signal}}
In the framework of full-Bayes methods we analyse the effect of the reference model using two continuous hierarchical shrinkage priors: the Dirichlet-Laplace \citep{paper:dirichlet_laplace} and the regularised horseshoe prior \citep{paper:rhs}. Although the horseshoe+ prior by \cite{paper:horseshoe+} is a state-of-the-art prior for sparse signal analysis in the context of the normal means problem, we decided to include the regularised horseshoe due to its faster MCMC inference, since our purpose in this paper is not to study the best prior choice, but rather compare and show the benefits of using a reference model when carrying out variable selection. We used an uniform prior on $(1/p,1/2)$ for the Dirichlet hyperparameter of the Dirichlet-Laplace prior, whereas regarding the reguelarised horseshoe prior we followed the indication provided in \cite{paper:rhs}, setting the prior guess of the effective number of parameters equal to 1 to achieve the highest shrinkage. Yet we have not observed any sensibility of the results due to such a choice.

@@

Figure \ref{fig:posterior_intervals} shows an example of posterior distributions for the model \eqref{eq:normal_means_problem2} using the regularised horseshoe prior. Respectively on the right and on the left the results using or not the reference model approach. It is evident how the reference model helps in tearing apart the signals from the noise, resulting in less biased estimates. This is quantified in Figure \ref{fig:SESE_SSE} where average SESE and SSE are depicted after 100 simulations. We observe that the reference approach (in orange) has a clear lower error estimate for both the SESE and the SSE. As $n$ and $\rho$ grow, the amount of error diminish, as expected, due to a larger amount of information of the relevance of each variable provided by the data. We also note that the two priors seem to achieve very similar results, regardless of the approach used.
